Data preparation

### 2020-07-02 production/prod_prep-data.rmd
data-analisis-metodologia
En esta version se presenta un proseamiento de datos que utiliza solo un codigo, y no distintos documentos como en la version anterior.

se incorpora metodologia en paper.

Se incorporo analisis multinivel, pendientes aleatorias e interacciones entre niveles.

por agregar:
bibliografia y citarla con zotero.
analisis por resultado.
discucion.
resumen.

---
title: "Data preparation"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/bib/style.css"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---

@@

load packages
```{r}
library(sjPlot)
library(sjmisc) # several functions,ej read_stata
library(descr)
library(memisc)  # codebook
library(psych) # cor2latex
library(corrplot) # graph correlations
library(lavaan)
library(stargazer)
library(semTools)
library(plyr) # count
library(dplyr)
#library(car) # recode
library(ggplot2)
#library(Hmisc)
library(tidyverse)
library(data.table)
library(stringr)
library(countrycode)
library(lme4)
library(texreg)
library(mice)
library(ggrepel) # for scatter labels in sjp.scatter
#library(semPlot)
library(haven)
library(sjlabelled)
library(kableExtra)
library(summarytools)

#library(Hmisc)
```

# Open data and General setting

```{r}
issp2009=read_stata("input/data/original/ZA5400_v4-0-0.dta")

    # Check data  
    #names(issp2009)
```

```{r}
names(issp2009) <- tolower(names(issp2009)) # change to small
```

## Check & generate IDs (v4: respondent, v5: country)

# Generate new sequential id individuals by country to merge
      issp2009$id <- sequence(tabulate(issp2009
                                     $v5))
    issp2009$idtem=issp2009$v5*10000  
    issp2009$id=issp2009$idtem + issp2009$id
```

# Measurement Merit & Getting ahead

Note: object now generated from different
script (merit_per_pref.R; merit_per_pref.rda)

##  Measurement and Redistribution

##  Data preparation, gen redistrib.rda

| Code | New Code   | Variable                                                                                                        |
|------|------------|-----------------------------------------------------------------------------------------------------------------|
| v33  | income_dif | Gov. resp to reduce differences in income                                                                       |
| v34  | unemployed | Gov. resp to provide decent s andard of living for unemployed                                                   |
| v36  | taxes      | People with high income should pay a larger / same smaller share of income in taxes than those with low income |
| v38  | health     | ok if people with high income can buy better health                                                             |
| v39  | educ       | ok if people with high income can buy better education                                                          |                                                         |
###  Rename & define object

@@

    stargazer(redistrib[-c(1,2)], type="html")

@@

### adjust labels NAs
```{r}
     get_labels(redistrib$income_dif)
    redestrib <-sjlabelled::set_na(redistrib[,c("income_dif","unemployed", "taxes", "health", "educ")], na = c(8,9))

@@

### Aggregated data **x**

  # Dataset with original code for sjp.likert graph
      redistrib2=redistrib

  # Reverse code for SEM models
      redistrib[3:7]=6-redistrib[3:7]

  # Checks
redistrib_agg <- aggregate(redistrib, by=list(redistrib$v5), FUN=mean,na.rm=TRUE)

# En analisis me falta esta base de datos, no estoy seguro de como debe guardarse.

  # Save object
     # save(redistrib, file="input/data/proc/redistrib.rda")

@@

### General Check "redistrib.rda"
```{r}
print(dfSummary(redistrib_agg, valid.col = FALSE, graph.magnif = 1),
      max.tbl.height = 300, method = "render")
```

```{r}
#############################################
# Ver donde va este codigo. (agregar a prodcution)
###################################################################################################################### 2.5 Invariance
  #   measurementInvariance(cfa_2, data = redistrib.agg, group = "v5")      # No funciono la invarianza arreglar.

@@

 End sec 2; saved objects
 # redistrib.rda: clean & recoded
 # redistrib_sco.rda : fac scores   [por ahora en analysis]
 # __propuesta__ redistrib.agg

# Preparation Individual & Macro variables.

## Individual level variables

```{r}
  indepvar=issp2009
#length(indepvar$id)
```

### Recode sex
```{r}
# Sex
sjPlot::plot_frq(indepvar$sex, title ="Before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sjPlot::plot_frq(indepvar$sex, title ="After")
```

### Recode Age
```{r}

label<- c("")
label<- "1"
  # Age
sjPlot::plot_frq(indepvar$age, title = "Before",show.mean = T , show.values = F,show.n = F, axis.labels =)

@@

sjPlot::plot_frq(indepvar$age_c, title = "After", show.na = T)

@@

```{r}
sjPlot::plot_frq(indepvar$degree, coord.flip = TRUE, title = "Before")
```

```{r}
  # Recode. Values over 5 are removed

@@

#### Dummy university
```{r}
# Dummy university
  indepvar$univ=indepvar$degree
  indepvar$univ=ifelse(indepvar$univ<=4,0,
  ifelse(indepvar$univ==5,1,NA))

@@

### Recode Income
```{r results='asis'}
  stargazer(indepvar[182:222], type="html")
```

```{r results='asis'}
  # Income (variables finish in _inc)
# Continuo

   # Recode missings
      # Para todos los paises, recode missings.  
      indepvar[182:222][indepvar[182:222] >= 9999990] <- NA
      indepvar[182:222][indepvar[182:222] == 999990] =NA
      indepvar[182:222][indepvar[182:222] == 999997] =NA
  indepvar[182:222][indepvar[182:222] == 999998] =NA
  indepvar[182:222][indepvar[182:222] == 999999] =NA

    # Identificar ceros (para poder diferenciar de los NAs luego)
    indepvar[182:222][indepvar[182:222] == 0] <- 111111

  # Agregar ahora todos en un solo vector
indepvar$income=rowSums(indepvar[182:222],na.rm = TRUE)

@@

stargazer(indepvar[182:222], type="html")

```{r}
summary(indepvar$income)
```

@@

```{r}
# Household income

@@

summary(indepvar$hhincome)
```

```{r}
# check
income=indepvar[c("v5", "ar_inc", "hompop","income",
"hhincome")]
# View(income)

@@

# Check
prop.table(table(indepvar$v5,indepvar$quintile),1)*100

```{r}
# Generar quintiles con NA como categorÃ?a
indepvar$quintile_miss=indepvar$quintile
indepvar$quintile_miss[is.na(indepvar$quintile_miss)] = 6

summary(indepvar$quintile_miss)
```

### Recode Subjetive status
```{r}

@@

# Home value (ver Nota 3)
summary(indepvar$v67)

@@

```{r}
  # Party
    #freq(issp2009$party_lr)
#prop.table(table(indepvar$v5,indepvar$party_lr),1)*100
# paises sin datos: CL, CN, CY, HU, IL, TW
#freq(indepvar$cl_prty) # estan
#freq(indepvar$cn_prty) # no
#freq(indepvar$cy_prty) # si
#freq(indepvar$hu_prty) # si
#freq(indepvar$il_prty) # si
#freq(indepvar$tw_prty) # si

@@

## Indep macro var

### Load
```{r}
# Inequality swiid (4)        
swiid = read_stata("input/data/original/swiid8_2.dta")

# convertir desde formato original list a dataframe
#swiid_summary <- swiid %>%  bind_rows() %>%
#group_by(country, year) %>%  
#summarize_all(funs(mean, sd)) %>%
#ungroup() %>% rename(.dots=setNames(names(.),
#str_replace(names(.), "_mean", ""))) %>%  
#rename_(.dots=setNames(names(.),
 #     str_replace(names(.), "_sd", "_se")))

@@

###  Filter only 2009
```{r}
#summary(swiid_summary$.dots...year)

#swiid_summary09=subset(swiid_summary, .dots...year==2009)

@@

###  Merge with indepvar object
```{r}
# Generate equivalente country code

#head(swiid_summary09$.dots...country)
#as.numeric(swiid_summary09$country)

# Continuo
#swiid_summary09$v5=countrycode(swiid_summary09$.dots...country,'country.name','iso3n')
#str(swiid_summary09$v5)

# Categórico
#swiid_summary09$v5c=countrycode(swiid_summary09$.dots...country,'country.name','iso3c')
#str(swiid_summary09$v5c)

# Merge
#indepvar <- merge(swiid_summary09,indepvar,by=c("v5"))
#summary(indepvar$.dots..._1_gini_disp)

@@

#### agregate ========
```{r}
# aggregate(indepvar[c("v5","gini_net")],list(indepvar$v5c.x,indepvar$.dots...country),mean) #Buscar como #agregar la variable
```

@@

# Quality of government
# los objetos se generan en la sintax qog_explore

# Merge qog
load("input/data/proc/qog_merit.rda")
names(qog_merit)
indepvar <- merge(qog_merit,indepvar,by=c("v5"))
# #freq(indepvar$wdi_gini)

# Generate object
# save(indepvar, file="input/data/proc/indepvar.rda")
#
##
#

@@

End sec 3 objeto: indepvar.rda -------

```{r}
load(file = "input/data/proc/indepvar.rda")

print(dfSummary(indepvar, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

#  MODELS B: PREFERENCES

# 5.1 Data preparation

  # Load & merge

 load("input/data/proc/indepvar.rda")

 load("input/data/proc/redistrib.rda")
 load("input/data/proc/redistrib_sco.rda")
length(redistrib$accum)

### aggregate(redistrib[c("redist","accum")],by=list(v5),FUN=mean, na.rm=TRUE)

# Check legths for merge

 # Merge  (to the x, indepvar, largest)
 pref=merge(redistrib_sco, indepvar, by=c("id"), all.x = TRUE)
 #names(pref)

# Check
# dim(pref)
#length(pref$v5.x)
#  aggregate(pref[c("v5.x","gini_net","redist")],list(pref$country, pref$v5c),mean, na.rm=TRUE)

#  mean(pref$redist, na.rm=TRUE)
# pref$v5=pref$v5.x
#  
#  summary(pref$redist)
#  summary(pref$id)

# Generate level 2 aggregated vars
# names(pref)
# agg_lm=aggregate(pref[c(4:10,22:42)], by=list(pref$v5),FUN=mean, na.rm=TRUE)

# names(agg_lm)
# dim(agg_lm)

# colnames(agg_lm) <- paste("j", colnames(agg_lm), sep = "_")
#  table(agg_lm$v5=agg_lm$j_v5)

#  pref2=merge(pref,agg_lm, by="v5")
# pref=pref2
#  dim(pref)

# Group mean centering
  #  pref$age_g=age-j_age
  #  pref$sex_g =sex-j_sex
  #  pref$univ_g =univ-j_univ
  #  pref$sstatus_g= sstatus-j_sstatus
  #  
  #  summary(pref$univ_g)
  #  names(pref)

  # Save
  #  save(pref, file = "input/data/proc/pref.rda")

@@

```{r}
# 6.1 Data preparation - meritocracy.rda

  # Load & merge
#  load("input/data/proc/getahead.rda")
#  load("input/data/proc/indepvar.rda")
#  #names(indepvar)
#  load("input/data/proc/merit_per_pref_sco.rda")
# #names(merit_per_pref_sco)
#
# Check legths for merge
# length(indepvar$id)
# summary(indepvar$id)
#  length(getahead$id)
#  summary(getahead$id)

 # Merge  (to the x, indepvar, largest)
#  meritocracy=merge(merit_per_pref_sco, indepvar, by=c("id"))
#  #names(meritocracy)

# # Check
#  dim(meritocracy)
# length(meritocracy$v5.x)
#  #aggregate(meritocracy[c("v5.x","gini_net","merit")],
 # list(meritocracy$country, meritocracy$v5.x),mean, na.rm=TRUE)
#  mean(meritocracy$merit, na.rm=TRUE)
#  meritocracy$v5=meritocracy$v5.x

# Generate level 2 aggregated vars
# names(meritocracy)
#agg_lm=aggregate(meritocracy,by=list(meritocracy$v5c),
# FUN=mean, na.rm=TRUE)
# names(agg_lm)
# dim(agg_lm)

# colnames(agg_lm) <- paste("j", colnames(agg_lm), sep = "_")
#   names(agg_lm)
#  agg_lm$v5=agg_lm$j_v5
#  meritocracy2=merge(meritocracy,agg_lm, by="v5")
#  dim(meritocracy2)
# meritocracy=meritocracy2
#  dim(meritocracy)

# Group mean centering
#    meritocracy$age_g=meritocracy$age-meritocracy$j_age
#    meritocracy$sex_g =meritocracy$sex-meritocracy$j_sex
#    meritocracy$univ_g =meritocracy$univ-meritocracy$j_univ
#  meritocracy$sstatus_g= meritocracy$sstatus-meritocracy$j_sstatus

#    summary(meritocracy$univ_g)
  #  names(meritocracy)

  # Save
 #   save(meritocracy, file = "input/data/proc/meritocracy.rda")

@@

```{r}
# Adjust data
    pref_agg=aggregate(pref, by=list(pref$v5c),
    	FUN=mean, na.rm=TRUE)
    names(pref_agg)[names(pref_agg)=="Group.1"] <- "v5c"

  # Macro descriptives

    hist(pref_agg$gini_net)
   table(pref_agg$accum)

    save(pref_agg, file = "input/data/proc/pref_agg.rda")
```

>>>>

---
title: "Data preparation"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/bib/style.css"
output:
  html_document:
    number_sections: false
    toc: true
    toc_float:
        collapsed: true
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---

@@

# Document content: Data preparation

In this site the production and adjustment of the databases that are used for the multilevel analysis are exposed. The work in general focuses on selecting and recoding variables obtained from international databases such as the International Social Survey (ISSP) and the Standardized World Income Income Inequality Database (SWIID). In addition, factor analyzes are performed to subsequently impute predicted values that represent the estimated latent variables.

In diagram 1, a summary of the data processing is presented, which starts from international databases (input) to processed databases. As shown in the graph, the document is divided into 4 sections , corresponding to the subtitles of the codes.

In the first section, in addition to selecting and recoding ISSP variables, factor analyzes are performed to evaluate and create the latent variables of preferences about redistribution and inequality. In section 2, international SWIID and GOQ data are collected and added together with ISSP data, which includes predicted values for latent variables of meritocratic perceptions and preferences. In the next two sections, adjustments are made for multilevel analyzes for the pref.rda and meritocracy.rda databases.

### load packages
```{r}
library(sjPlot)
library(sjmisc) # several functions,ej read_stata
library(descr)
library(memisc)  # codebook
library(psych) # cor2latex
library(corrplot) # graph correlations
library(lavaan)
library(stargazer)
library(semTools)
library(plyr) # count
library(dplyr)
#library(car) # recode
library(ggplot2)
#library(Hmisc)
library(tidyverse)
library(data.table)
library(stringr)
library(countrycode)
library(lme4)
library(texreg)
library(mice)
library(ggrepel) # for scatter labels in sjp.scatter
#library(semPlot)
library(haven)
library(sjlabelled)
library(kableExtra)
library(summarytools)
library(tidyselect)
library(magrittr)
library(semPlot)
#library(Hmisc)

# Section-1: Preparation individual variables ISSP

## General preparation
```{r results='hide'}
#issp2009=read_stata("input/data/original/ZA5400_v4-0-0.dta")
#save(issp2009, file="input/data/original/issp.rda")

load(url('https://raw.githubusercontent.com/franciscomeneses/bases/master/issp.rda'))

    # Check data  
    #names(issp2009)

### change variable names to lowercase
names(issp2009) <- tolower(names(issp2009))

### Check & generate IDs (v4: respondent, v5: country)
### Generate new sequential id individuals by country to merge
      issp2009$id <- sequence(tabulate(issp2009
                                     $v5))
    issp2009$idtem=issp2009$v5*10000  
    issp2009$id=issp2009$idtem + issp2009$id
```

##  Preparation-data of the redistributive preference scales: redistrib.rda

| Code | New Code   | Variable                                                                                                        |
|------|------------|-----------------------------------------------------------------------------------------------------------------|
| v33  | income_dif | Gov. resp to reduce differences in income                                                                       |
| v34  | unemployed | Gov. resp to provide decent s andard of living for unemployed                                                   |
| v36  | taxes      | People with high income should pay a larger / same smaller sha3re of income in taxes than those with low income |
| v38  | health     | ok if people with high income can buy better health                                                             |
| v39  | educ       | ok if people with high income can buy better education                                                          |                     Table:`Items for latent variables`

###  Rename & define object

@@

    stargazer(redistrib[-c(1,2)], type="html")  
```

@@

```{r}
dim(redistrib)
```

### adjust labels NAs
```{r}
     get_labels(redistrib$income_dif)
    redistrib[,3:7] <-sjlabelled::set_na(redistrib[,c("income_dif","unemployed", "taxes", "health", "educ")], na = c(8,9))

@@

### Reverse code for SEM models
```{r}
redistrib[3:7]=6-redistrib[3:7]

@@

### 2.4 Factor scores

```{r cache=TRUE, results='hide'}
cfa_red1 <- '
	# latent variables
	redist =~ income_dif + unemployed + taxes 
	accum  =~ health + educ
	'

	  # generate 5 multiple complete datasets 
		out <- mice(redistrib[3:7], m=5)

@@

```{r include=FALSE}

		D1 <- complete(out, 1) 
		D2 <- complete(out, 2) 
		D3 <- complete(out, 3) 
		D4 <- complete(out, 4) 
		D5 <- complete(out, 5)

		# fit model for each complete dataset 
		fit1 <- cfa(cfa_red1, data=D1) 
		fit2 <- cfa(cfa_red1, data=D2) 
		fit3 <- cfa(cfa_red1, data=D3) 
		fit4 <- cfa(cfa_red1, data=D4) 
		fit5 <- cfa(cfa_red1, data=D5)

	# predict scores for all models 
		p1 <- predict(fit1) 
		p2 <- predict(fit2) 
		p3 <- predict(fit3) 
		p4 <- predict(fit4) 
	p5 <- predict(fit5)

# compute 'average' across 5 sets of scores: 
		scores <- (p1 + p2 + p3 + p4 + p5)/5

 #Generate factor scores      
   scores_dat=as.data.frame(scores)

# Adaptar base para agregar factor scores (sacar todos NA)  
   redistrib_m=redistrib[rowSums(is.na(redistrib[3:7]))!=5,]

# Merge with factor scores
	  redistrib_sco=cbind(redistrib,scores)

	  # Check
	   stargazer(redistrib_sco[,8:9], type ="text")

	# Save  factor scores
	  save(redistrib_sco, file="input/data/proc/redistrib_sco.rda")
```

redistrib_sco [56021,9]

```{r}
print(dfSummary(redistrib_sco, valid.col = FALSE, graph.magnif = 1),
      max.tbl.height = 300, method = "render")
```

## Individual level variables: Sociodemograficas.

```{r results='asis'}
### Select

indepvar= issp2009 %>% dplyr::select(contains("_inc"), "sex","age","degree", "hompop", "v44", "v45", "v5","id")

### Recode sex

sjPlot::plot_frq(indepvar$sex, title ="Gender before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sjPlot::plot_frq(indepvar$sex, title ="gender after")

### Recode Age

  # Age
sjPlot::plot_frq(indepvar$age, title = "Age before",show.mean = T , show.values = F,show.n = F)

@@

sjPlot::plot_frq(indepvar$age_c, title = "Age after", show.na = T)

@@

sjPlot::plot_frq(indepvar$degree, coord.flip = TRUE, title = "Degree before")

  # Recode. Values over 5 are removed

@@

#### Dummy university
# Dummy university
  indepvar$univ=indepvar$degree
  indepvar$univ=ifelse(indepvar$univ<=4,0,
  ifelse(indepvar$univ==5,1,NA))

@@

### Recode Income

  stargazer(indepvar[1:41], type="html")

  # Income (variables finish in _inc)
# Continuo

   # Recode missings
      # Para todos los paises, recode missings.  
      indepvar[1:41][indepvar[1:41] >= 9999990] <- NA
      indepvar[1:41][indepvar[1:41] == 999990] =NA
      indepvar[1:41][indepvar[1:41] == 999997] =NA
  indepvar[1:41][indepvar[1:41] == 999998] =NA
  indepvar[1:41][indepvar[1:41] == 999999] =NA

    # Identificar ceros (para poder diferenciar de los NAs luego)
    indepvar[1:41][indepvar[1:41] == 0] <- 111111

  # Agregar ahora todos en un solo vector
indepvar$income=rowSums(indepvar[1:41],na.rm = TRUE)

@@

stargazer(indepvar[1:41], type="html")

summary(indepvar$income)

@@

# Household income

@@

#Wsummary(indepvar$hhincome)

# check
income=indepvar[c("v5", "ar_inc", "hompop","income",
"hhincome")]
# View(income)

@@

# Check
#prop.table(table(indepvar$v5,indepvar$quintile),1)*100

# Generar quintiles con NA como categorÃ?a
indepvar$quintile_miss=indepvar$quintile
indepvar$quintile_miss[is.na(indepvar$quintile_miss)] = 6

sjPlot::plot_frq(indepvar$quintile_miss, coord.flip = TRUE, title = "Quintiles de ingreso")
#stargazer(indepvar$quintile_miss, type = "html")

### Recode Subjetive status

@@

@@

Codigos por incorporar: se deben hacer ajustes de moneda y partidos por pais. 
```{r}
# Home value (ver Nota 3)
#summary(indepvar$v67)

  # Party
    #freq(issp2009$party_lr)
#prop.table(table(indepvar$v5,indepvar$party_lr),1)*100
# paises sin datos: CL, CN, CY, HU, IL, TW
#freq(indepvar$cl_prty) # estan
#freq(indepvar$cn_prty) # no
#freq(indepvar$cy_prty) # si
#freq(indepvar$hu_prty) # si
#freq(indepvar$il_prty) # si
#freq(indepvar$tw_prty) # si

@@

```{r}
#Eliminar income por paises. 
indepvar=indepvar[-c(1:41)]
dim(indepvar)
View(indepvar)
```

```{r}
#indepvar_graph<-as.data.frame(indepvar[,2:16])

print(dfSummary(indepvar[-c(7)], valid.col = FALSE, graph.magnif = 1),
      max.tbl.height = 300, method = "render")
```

## Measurement Merit & Getting ahead

| Code  	| New Code  	| Variable              	|
|-------	|-----------	|-----------------------	|
| v6    	| wealthy   	| wealthy family        	|
| v7    	| pareduc   	| educated parents      	|
| v9    	| ambition  	| ambition              	|
| v10   	| hwork     	| hard work             	|
| v11   	| people    	| right people          	|
| v12   	| polcone   	| political connections 	|
| v14   	| race      	| race                  	|
| v16   	| gender    	| gender                	|
| v5    	| -         	| Country               	|
| id    	| -         	| inividual id          	|

```{r results='hide'}
    # Rename
    getahead=issp2009[,c("v6","v7","v9", "v10","v11","v12",
             "v14","v16", # get ahead
    	  		 "v5","id")]

    getahead$wealthy=getahead$v6
    getahead$pareduc=getahead$v7
    getahead$ambition= getahead$v9
    getahead$hwork=getahead$v10
    getahead$people=getahead$v11
    getahead$polcone=getahead$v12
    getahead$race=getahead$v14
    getahead$gender=getahead$v16

    getahead=getahead[-c(1:8)]

  # recode values 8 9 to NA
    #freq(getahead$wealthy)
    getahead[3:10][getahead[3:10] > 5] <- NA
    #freq(getahead$gender) # check ok
    stargazer(getahead, type = "html")

  # adjust labels
    get_labels(getahead$wealthy)
    getahead[ , 3:10][getahead[ , 3:10] >= 8] <- NA
    get_labels(getahead[3:10]) # check

  # Reverse code for SEM models
    getahead[3:10]=6-getahead[3:10]

  # Generate variables with 3 values for getahead mess model categoric
    #names(getahead)
    getahead_temp=subset(getahead[c(2,3:10)])
    #names(getahead_temp)
    getahead_temp[2:9][getahead_temp[2:9] <  4] <- 3
   # freq(getahead_temp$hwork)
    #freq(getahead$hwork)

    colnames(getahead_temp)=paste("c3", colnames(getahead_temp),
    	sep="")
    names(getahead_temp)[names(getahead_temp)=="c3id"] <- "id"
    getahead_temp2=merge(getahead,getahead_temp, by=c("id"))
  	names(getahead_temp2) # ok
  	getahead=getahead_temp2

@@

```{r}
plot_likert((getahead[,3:8]), 
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "getahead",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )
```

```{r}
	# Save object
  #  save(getahead, file="../objects/getahead.rda")

@@

### Detearn: Data preparation, detearn.rda ----- #####

```{r results='hide'}
		#names(issp2009)
	  detearn=issp2009[,c("v47", "v48", "v49", "v50", "v51",
	   	"v52", "v5","id")]

    detearn$respons 	= detearn$v47
    detearn$yeduc  	  = detearn$v48
    detearn$family    = detearn$v49
    detearn$child     = detearn$v50
    detearn$welljob   = detearn$v51
    detearn$hardjob   = detearn$v52

	  #names(detearn)
    detearn=detearn[-c(1:6)]

  # recode values 8 9 to NA
    summary(detearn)
  # freq(detearn$respons)
    detearn[3:8][detearn[3:8] > 5] <- NA
   # freq(detearn$respons) # check ok

  # Out Portugal (no answer in well job item)
    detearn[which(detearn$v5==620),]=NA

  # adjust labels ###PROB PORTUCAL!!!

    get_labels(detearn)
detearn[ , 3:8][detearn[ , 3:8] >= 8] <- NA

    detearn$welljob<-sjlabelled::set_na(detearn$welljob, na =c(1))
    summary(detearn)
   # freq(detearn$welljob) ## prob portugal
    detearn$welljob[detearn$welljob ==0] = NA
    get_labels(detearn$welljob)
    labels(detearn$welljob)=labels(detearn$respons)### PROB NOT SOLVED

  # Dataset with original code for sjp.likert graph
    detearn2=detearn

  # Reverse code for SEM models

detearn$respons = as.numeric(6 - detearn$respons)
detearn$yeduc = as.numeric(6 - detearn$yeduc)
detearn$family = as.numeric(6 - detearn$family)
detearn$child = as.numeric(6 - detearn$child)
detearn$welljob = as.numeric(6 - detearn$welljob)
detearn$hardjob = as.numeric(6 - detearn$hardjob)
    #freq(detearn$respons)

	# Save object
#    save(detearn, file="detearn.rda")

    table(detearn[,4])
```

## Measuring Beliefs & Perceptions: merit_pref_perc

```{r}
# 3. MEASURING BELIEFS & PERCEPTIONS ------ -

# 3.1 Define object --------------------- -------------------------------

#			load("./objects/getahead.rda")
#			load("./objects/detearn.rda")
		#	names(getahead)
		#	names(detearn)

			merit_per_pref=merge(getahead,detearn, by=c("id","v5"))
		#	names(merit_per_pref)

  # Estimación del modelo c/ unmerit 2do orden
	  cfa_perpref2 <- '
	  # latent variables
	  merit =~ hwork + ambition
	  parent=~ wealthy + pareduc
	  backg=~ race + gender
		network=~ people + polcone
		unmerit=~ parent + backg + network # 2nd order
	  bmerit =~ welljob + hardjob
	  need=~ family + child
	  '
	  fit_perpref2 <- cfa(cfa_perpref2,data=merit_per_pref,
	  	missing = "ML")
#	  summary(fit_perpref2, fit.measures=TRUE,standardized=TRUE)

  # Path model
		  semPaths(fit_perpref2,layout = "tree", rotation = 2,
		  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
		  	sizeMan = 3.5, sizeLat = 6)
```

### Factor scores fit_perpref2: merit_per_pref_sco

```{r cache=TRUE, results='hide'}

			out <- mice(merit_per_pref[,c(3:10,19:24)], m=5)
```

```{r results='hide'}
		# Multiple imputation (para recuperar missings en scores) - REVIEW THIS, command lavPredict from 2017 should predict with missing values therefore saving from multiple imputation

		  # generate 5 multiple complete datasets

			D1 <- complete(out, 1)
			D2 <- complete(out, 2)
			D3 <- complete(out, 3)
			D4 <- complete(out, 4)
			D5 <- complete(out, 5)

			# fit model for each complete dataset
			fit1 <- cfa(cfa_perpref2, data=D1)
			fit2 <- cfa(cfa_perpref2, data=D2)
			fit3 <- cfa(cfa_perpref2, data=D3)
			fit4 <- cfa(cfa_perpref2, data=D4)
			fit5 <- cfa(cfa_perpref2, data=D5)

		# predict scores for all models
			p1 <- predict(fit1)
			p2 <- predict(fit2)
			p3 <- predict(fit3)
			p4 <- predict(fit4)
			p5 <- predict(fit5)

		# compute 'average' across 5 sets of scores:
			scores <- (p1 + p2 + p3 + p4 + p5)/5

	  # Generate factor scores
	    scores_dat=as.data.frame(scores)
	    dim(scores_dat)
	    str(scores_dat)
	    summary(scores)

		# Generate object with factor scores
	    dim(merit_per_pref)
	    dim(scores_dat)
		  merit_per_pref_sco=cbind(merit_per_pref,scores)

	# Save object with factor scores
	#	names(merit_per_pref_sco)
		merit_per_pref_sco=merit_per_pref_sco[,c(1:2,25:31)]
#	  save(merit_per_pref_sco,
#	  	file="./objects/merit_per_pref_sco.rda")

@@

Bases de datos creadas.

Indepvar.rda: variables sociodemograficas
redistrib_sco: variables latentes de preferencias redistributivas.
merit_perc_pref_sco: variables latentes de creencias meritocraticas.

## Merge varaibles indivuales.

@@

indiv<- merge (indepvar, redistrib_sco, by = c("id"))

indiv <- merge (indiv,  merit_per_pref_sco, by = c("id"))
```

```{r}
print(dfSummary(indiv, valid.col = FALSE, graph.magnif = 1),
      max.tbl.height = 300, method = "render")
```

```{r}
save(indiv, file="input/data/proc/indiv.rda")
```

# Section 2: agregar datos

```{r}
agg_lm=aggregate(indiv, by=list(indiv$v5),FUN=mean, na.rm=TRUE)

colnames(agg_lm) <- paste("j", colnames(agg_lm), sep = "_")
table(agg_lm$j_v5)

agg_lm$v5=agg_lm$j_v5

mer_pref=merge(indiv,agg_lm, by="v5")

 dim(mer_pref)

@@

```{r}
    mer_pref$age_g=mer_pref$age-mer_pref$j_age
    mer_pref$sex_g =mer_pref$sex-mer_pref$j_sex
    mer_pref$univ_g =mer_pref$univ-mer_pref$j_univ
  mer_pref$sstatus_g= mer_pref$sstatus-mer_pref$j_sstatus

    summary(mer_pref$univ_g)
```

# Seccion 3:  add macro var

## Section 2.1: SWIID
```{r}
# Inequality swiid (4)        
load(url("https://raw.githubusercontent.com/franciscomeneses/bases/master/swiid8_3.rda"))

# convertir desde formato original list a dataframe

swiid_summary <- swiid %>%  bind_rows() %>%
group_by(country, year) %>%  
summarize_all(funs(mean, sd)) %>%
ungroup() %>% dplyr::rename(.dots=setNames(names(.),
str_replace(names(.), "_mean", ""))) %>%  
dplyr::rename_(.dots=setNames(names(.),str_replace(names(.), "_sd", "_se")))

save(swiid_summary, file = "input/data/proc/swiid_summary.rda")

#load( file= "input/data/proc/swiid_summary.rda")
```

###  Filter only 2009
```{r}
summary(swiid_summary$.dots...year)

swiid_summary09=subset(swiid_summary, .dots...year==2009)
```

###  Merge with indepvar object

```{r}
# Generate equivalente country code

head(swiid_summary09$.dots...country)
as.numeric(swiid_summary09$country)

# Continuo
swiid_summary09$v5=countrycode(swiid_summary09$.dots...country,'country.name','iso3n')
str(swiid_summary09$v5)

# Categórico
swiid_summary09$v5c=countrycode(swiid_summary09$.dots...country,'country.name','iso3c')
str(swiid_summary09$v5c)

# Merge
#indepvar <- merge(swiid_summary09,indepvar,by=c("v5"))

#summary(indepvar$.dots..._1_gini_disp)

@@

```{r}
mer_pref<- merge(swiid_summary09,mer_pref, by=c("v5"))
```

## Section 2.2: Qog
```{r}
# No entiendiendo bien este codigo, no guarda en ninguna parte y genera solo un output.

#aggregate(indepvar[c("v5","gini_net")],list(indepvar$v5c.x,indepvar$.dots...country),mean) #Buscar como #agregar la variable 
```

```{r results='hide'}

# Quality of government
#qog=read_stata("input/data/original/qog_std_ts_jan17.dta")	
#save(qog, file = "input/data/original/qog.rda")

load(url('https://raw.githubusercontent.com/franciscomeneses/bases/master/qog.rda'))

		# Extract 2009 data
			qog2009=subset(qog, year==2009)

		# Merge with ISSP countries for cleaning

			load("input/data/proc/indepvar_contries.rda")
			issp_countries=	aggregate(indepvar_contries[c("v5")], 
					list(indepvar_contries$country,indepvar_contries$v5c),mean)

			qog2009[c("ccode","cname")] # check ISO codes
			names(qog2009)[names(qog2009) == 'ccode'] <- 'v5'
			qog2009_c=merge(issp_countries, qog2009, by=c("v5")) 
			dim(qog2009_c)
			colSums(is.na(qog2009_c))

			# Eliminar columnas con máximo 5 NAs
			qog2009_c_na= qog2009_c[ , colSums(is.na(qog2009_c)) < 6]

			qog2009_c_na= qog2009_c_na %>% dplyr::select("v5", "fi_index") %>% as.data.frame()
			#names(qog2009_c_na)

@@

# Merge
```{r}

mer_pref <- merge(mer_pref, qog2009_c_na, by=c("v5"))
```

End sec 2 objeto: mer_pref.rda -------

```{r}
mer_pref$gini_neto<- mer_pref$.dots...gini_disp
mer_pref$gini_mkt <- mer_pref$.dots...gini_mkt
```

```{r}
save(mer_pref, file="input/data/proc/mer_pref.rda")
```

```{r}
mer_pref_polycor <- mer_pref %>% dplyr::select("j_merit","j_unmerit","j_bmerit","j_need",".dots...gini_disp",".dots...gini_mkt","fi_index")
save(mer_pref_polycor, file ="input/data/proc/mer_pref_polycor.rda")
```
